Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-09 paper/abstract.tex
Revise introduction

\begin{abstract}
    Bayesian optimization methods are promising for the optimizations of black-box functions that are expensive to evaluate. In this paper, a novel batch Bayesian optimization approach is proposed. The parallelization is realized via a multi-objective ensemble of multiple
    acquisition functions. In each iteration, the multi-objective optimization of the multiple acquisition functions is performed to search for
    the Pareto front of the acquisition functions. The batches of inputs are then selected from the Pareto front. The Pareto front represents the best trade-off between the multiple acquisition functions. Such a policy for batch Bayesian optimization can significantly improve the efficiency of optimization. The proposed method is compared with several
    state-of-the-art batch Bayesian optimization algorithms using analytical
    benchmark functions and real-world analog circuits. The experimental
    results show that the proposed method is competitive compared with the
    state-of-the-art algorithms.
\end{abstract}

>>>>

\begin{abstract}
    Bayesian optimization methods are promising for the optimization of black-box functions that are expensive to evaluate. In this paper, a novel batch Bayesian optimization approach is proposed. The parallelization is realized via a multi-objective ensemble of multiple
    acquisition functions. In each iteration, the multi-objective optimization of the multiple acquisition functions is performed to search for
    the Pareto front of the acquisition functions. The batches of inputs are then selected from the Pareto front. The Pareto front represents the best trade-off between the multiple acquisition functions. Such a policy for batch Bayesian optimization can significantly improve the efficiency of optimization. The proposed method is compared with several
    state-of-the-art batch Bayesian optimization algorithms using analytical
    benchmark functions and real-world analog integrated circuits. The experimental
    results show that the proposed method is competitive compared with the
    state-of-the-art algorithms.
\end{abstract}

### 2018-02-09 paper/intro.tex
Revise introduction

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems. The aim is to find the optimal design parameters that provide the
best circuit performance, which can be represented by a figure of merit (FOM)
scalar real-valued function. Prior works about analog circuit optimization
include offline model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
global models of the FOM via manual calculation or regression with simulated
data and then optimize the cheap-to-evaluate models. The problem with this
approach is that the accurate models are usually hard to get. For example,
in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
a sparse polynomial model for an amplifier circuit with ten design parameters.

@@

In recent years, the Gaussian process (GP)~\cite{GPML} model has been
introduced for the automated design of analog circuits to reduce the
required number of circuit simulations. In~\cite{liu2014gaspad}, GP is combined
with differential evolution algorithm. Recently, the Bayesian optimization
(BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization
algorithm is firstly introduced for the single- and multi-objective
optimization of general analog circuits and has shown to be more efficient
compared with other simulation-based approaches. In~\cite{wang2017efficient},
the Bayesian optimization algorithm is combined with adaptive Monte-Carlo
sampling to optimize the yield of analog circuits and static random-access
memory (SRAM).

@@

The Bayesian optimization algorithm has been extended to enable batch
selection. Some prior works, like the qEI \cite{qEI}, qKG \cite{wu2016parallel}
and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
approaches, consider to search for the optimal batch selection for a given
acquisition function. These methods usually involve some approximations or
Monte-Carlo sampling, and thus scales poorly as the batch size increases. Other
works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
batch-UCB (BUCB, BLCB for minimization
problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
exploration (GP-UCB-PE)~\cite{contal2013parallel} method, and the local
penalization (LP)~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
strategies that select individual points until the batch is filled.

@@

The MACE algorithm is tested using several analytical benchmark functions and
two real-world analog circuits, including an operational amplifier with ten
design parameters and a class-E power amplifier with twelve design parameters.
The BLCB method~\cite{desautels2014parallelizing}, local penalization method with expected improvement
acquisition function (EI-LP)~\cite{gonzalez2016batch}, qEI \cite{qEI} methods and qKG \cite{wu2016parallel} are compared with
MACE. The proposed MACE method achieved competitive performance when compared
with the state-of-the-art algorithms listed in the paper.

>>>>

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems. The aim is to find the optimal design parameters that provide the
best circuit performance, which can be represented by a figure of merit (FOM)
real-valued function. Prior works about analog circuit optimization
include offline model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
global models of the FOM via manual calculation or regression with simulated
data and then optimize the cheap-to-evaluate models. The problem with this
approach is that the accurate models are usually hard to get. For example,
in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
a sparse polynomial model for an amplifier circuit with ten design parameters.

@@

In recent years, the Gaussian process (GP)~\cite{GPML} model has been
introduced for the automated design of analog circuits to reduce the
required number of circuit simulations. In~\cite{liu2014gaspad}, GP is combined
with differential evolution algorithm. Recently, the Bayesian optimization
(BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization
algorithm is firstly introduced for the single- and multi-objective
optimization of general analog circuits and has shown to be much more efficient
compared with other simulation-based approaches. In~\cite{wang2017efficient},
the Bayesian optimization algorithm is combined with adaptive Monte-Carlo
sampling to optimize the yield of analog circuits and static random-access
memory (SRAM).

@@

The Bayesian optimization algorithm has been extended to enable batch
selection. Some prior works, like the qEI \cite{qEI}, qKG \cite{wu2016parallel}
and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
approaches, consider to search for the optimal batch selection for a specific
acquisition function. These methods usually involve some approximations or
Monte-Carlo sampling, and thus scale poorly as the batch size increases. Other
works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
batch-UCB (BUCB, BLCB for minimization
problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
exploration (GP-UCB-PE)~\cite{contal2013parallel} method, and the local
penalization (LP)~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
strategies that select individual points until the batch is filled.

@@

The MACE algorithm is tested using several analytical benchmark functions and
two real-world analog circuits, including an operational amplifier with ten
design parameters and a class-E power amplifier with twelve design parameters.
The BLCB method~\cite{desautels2014parallelizing}, local penalization method with expected improvement
acquisition function (EI-LP)~\cite{gonzalez2016batch}, qEI \cite{qEI} and qKG \cite{wu2016parallel} methods are compared with
MACE. The proposed MACE method achieved competitive performance when compared
with the state-of-the-art algorithms listed in the paper.
